 

### 2021-04-07 doc/manuscript/tables_figures/tables.Rmd
switch table order
work on table 1

  #pack_rows("Annual growth is simultaneously influenced by water, temperature, DBH, and time. ", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("How does climate shape tree growth? ", 1,12, latex_gap_space = "1em", italic= TRUE)%>%
  row_spec(c(1,5,10), bold = T) %>%
  add_indent(c(2:4, 6:9,11:12)) %>%
  pack_rows("How does growth rate vary as trees grow?", 13,17,italic= TRUE, latex_gap_space = "1em", hline_before = FALSE)%>%
  row_spec(c(13), bold = T) %>%
  add_indent(c(14:17)) %>%
  pack_rows("How have growth rates changed through time?", 18,21,italic= TRUE, latex_gap_space = "1em", hline_before = FALSE)%>%
  row_spec(c(18), bold = T) %>%
  add_indent(c(19:21)) %>%

>>>>

  #pack_rows("Annual growth is simultaneously influenced by water, temperature, DBH, and time. ", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("How do precipitation (P) and temperature (T) jointly shape tree growth? ", 1,12, latex_gap_space = "1em", italic= TRUE)%>%
  row_spec(c(1,5,10), bold = T) %>%
  add_indent(c(2:4, 6:9,11:12)) %>%
  pack_rows("How does growth rate vary with stem diameter (DBH)?", 13,17,italic= TRUE, latex_gap_space = "1em", hline_before = FALSE)%>%
  row_spec(c(13), bold = T) %>%
  add_indent(c(14:17)) %>%
  pack_rows("How have growth rates changed through time?", 18,21,italic= TRUE, latex_gap_space = "1em", hline_before = FALSE)%>%
  row_spec(c(18), bold = T) %>%
  add_indent(c(19:21)) %>%
